% Data/Code Availability, Acknowledgements, Author Contributions and Competing Interests

\section{Code and Data Availability}
Essential source code and data required to replicate the study's results-including VASP input files,
structure files of SACs, eDOS arrays and the pretrained CNN model-are available on GitHub repository
at \url{https://github.com/DanielYang59/cnn4dos}, and can be provided by the corresponding authors upon request.
Due to their substantial size in terabytes, the complete source data (complete VASP output files and such)
is not currently hosted on publicly available repositories,
but can be obtained from the corresponding authors upon request.

\section{Acknowledgements}
The QUT eResearch Office provided computational resources and services used in this work.
This research was undertaken with the assistance of resources and services from
the National Computational Infrastructure (NCI), supported by the Australian Government.
It was also supported by resources provided by the Pawsey Supercomputing Research Centre
with funding from the Australian Government and the Government of Western Australia.
Insights into deep learning methodologies were contributed by Mr. Yanwei Guan
from Chongqing University and Mr. Zhipeng He from Assoc. Prof. Chun Ouyang's team at QUT.
The machine learning and data analysis implementation benefited from
resources provided by the GitHub, TensorFlow and Stack Overflow communities.
Dr. Ryky Nelson from RWTH Aachen University offered valuable guidance on
Crystal Orbital Hamilton Population analysis.

\section{Author Contributions}
H.Y. performed DFT calculations, implemented Python code for
machine learning methodologies and data analysis,
and drafted and refined the manuscript.
J.Z. engaged in valuable discussions on DFT calculations.
Q.W. provided advice on the computer code revisions.
W.L. facilitated resource acquisition and offered research supervision.
B.L. provided guidance on DFT calculations and offered research supervision.
Z.S. initiated the research concept, contributed to manuscript revisions, and supervised the overall research.
T.L. guided DFT calculations and data analysis, offering continuous supervision
throughout the research and manuscript drafting.

\section{Competing Interests}
The authors declare no competing interests in relation to this research.
